\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{graphicx,scalerel}
\usepackage[utf8]{inputenc}
\usepackage{graphicx,xcolor,fontawesome}
\usepackage{makecell}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{\sectionspacing}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands

\newcommand\ssbullet[1][.6]{\mathbin{\ThisStyle{\vcenter{\hbox{%

          \scalebox{#1}{$\SavedStyle\bullet$}}}}}%
}
\renewcommand{\labelitemii}{\(\ssbullet\)}
\renewcommand\cellalign{rc}

% Common spacing parameters
\newcommand{\itemspacing}{-2pt}
\newcommand{\subitemspacing}{1pt}
\newcommand{\subheadingspacing}{-2pt}
\newcommand{\sectionspacing}{-15pt}

% Base item command that others can build upon
\newcommand{\baseItem}[2][\itemspacing]{
  \item\small{
    {#2 \vspace{#1}}
  }
}

% Unified list environment commands
\newcommand{\customListStart}[1][\itemspacing]{
  \begin{itemize}[leftmargin=*,label={}]
  \setlength{\itemsep}{5pt}
}
\newcommand{\customListEnd}[1][\itemspacing]{
  \end{itemize}\vspace{#1}
}

% Unified subheading command
\newcommand{\customSubheading}[6]{
  \vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    #1 & #2 \\
    #3 | \textit{#4} & \small {#5} \\
    #6
  \end{tabular*}\vspace{\subheadingspacing}
}

% Resume-specific commands
\newcommand{\resumeItem}[1]{\baseItem{#1}}
\newcommand{\resumeSubItem}[1]{\baseItem[\subitemspacing]{#1}}

\newcommand{\resumeSubheading}[5]{
  \customSubheading{\textbf{#1}}{#2}{#3}{#4}{#5}{}
}

\newcommand{\resumeConsultingSubheading}[5]{
  \vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    #3 | #4 & \small {#5} \\
  \end{tabular*}\vspace{\subheadingspacing}
}

\newcommand{\clientProjectHeader}[2]{
  \item\small{
    \textbf{#1} | \textit{#2} \vspace{-1pt}
  }
}

\newcommand{\clientProjectSubItem}[1]{
  \begin{itemize}[leftmargin=15pt, rightmargin=0pt, topsep=0pt, itemsep=1pt]
    \item\small{#1}
  \end{itemize}
  \vspace{-1pt}
}

\newcommand{\resumePromotionSubheading}[6]{
  \vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    #3 & \small {#4} \\
    #5 & \small {#6} \\
  \end{tabular*}\vspace{\subheadingspacing}
}

\newcommand{\resumeSubHeadingListStart}{\customListStart}
\newcommand{\resumeSubHeadingListEnd}{\customListEnd}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{\subheadingspacing}}

% Project-specific commands
\newcommand{\projectItem}[1]{\baseItem{#1}}
\newcommand{\projectSubItem}[1]{\baseItem[\subitemspacing]{#1}}

\newcommand{\projectSubheading}[5]{
  \customSubheading{\href{#4}{\textbf{#1}}}{#5}{#3}{\textit{#2}}{}{}{}
}

\newcommand{\projectSubHeadingListStart}{\customListStart}
\newcommand{\projectSubHeadingListEnd}{\customListEnd}
\newcommand{\projectItemListStart}{\begin{itemize}}
\newcommand{\projectItemListEnd}{\end{itemize}\vspace{\subheadingspacing}}

% Skills-specific command
\newcommand{\skillsItem}[1]{\baseItem[-5pt]{#1}}

% Enhanced icon command with color parameter
\newcommand{\seticon}[2][black]{\textcolor{#1}{\csname #2\endcsname}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{center}
  \textbf{\huge{Maaz Hashmi}} \\
  \vspace{10pt}
  \seticon{faGlobe} \href{https://maazh.tech}{Website}\qquad
  \seticon{faGithub} \href{https://github.com/maazh10}{GitHub}\qquad
  \seticon{faLinkedinSquare}
  \href{https://www.linkedin.com/in/maaz-hashmi-526a82222/}{LinkedIn}\qquad
  \seticon{faEnvelope}
  \href{mailto:mhashmi373@gmail.com}{mhashmi373@gmail.com}\qquad
  \seticon{faPhoneSquare} +1 (431) 338-6120\qquad
  \seticon{faMapMarker} Toronto, ON
\end{center}
\vspace{1pt}

%--------SKILLS------------
\section{Skills}
\resumeSubHeadingListStart
\skillsItem
{\textbf{Languages:} Python, Java, JavaScript/TypeScript, C, SQL}
\skillsItem
{\textbf{Frameworks:} Angular, React / React Native, Django, Next.js, Node.js, Express.js, Flask, SpringBoot}
\skillsItem{\textbf{Data/Databases:} MySQL, PostgreSQL, MSSQL, SQLite, MongoDB, Elasticsearch, Databricks}
\skillsItem
{\textbf{Cloud/DevOps:} Kubernetes, Azure, AWS, GCP, Terraform, GitHub Actions}
\skillsItem
{\textbf{Dev Tools:} Git, Docker, Maven, Jira}
\resumeSubHeadingListEnd
\vspace{5pt}

%-----------EXPERIENCE-----------------
\section{Work Experience}

\resumeSubHeadingListStart

\resumePromotionSubheading
{Electric Mind | Business \& Technology Consulting}{Toronto, ON}
{Software Developer II}{Jan. 2026 -- Present}
{Software Developer I}{Aug. 2024 -- Dec. 2025}
\resumeItemListStart
\clientProjectHeader
{RBC Investor Services}
{Angular, SpringBoot, Elasticsearch}
\clientProjectSubItem
{Diagnosed and fixed a release-blocking concurrency bug by uncovering thread-unsafe singleton session state in the backend, preventing intermittent server errors during concurrent API calls and stabilizing client launch.}
\clientProjectSubItem
{Drove a \textbf{97\%} reduction in dashboard load time (\textbf{20s} → \textbf{600ms}) by identifying and eliminating excessive JavaScript/CSS bundle bloat caused by repeated global style imports in Angular components; solution was shared across teams and adopted to optimize other platform micro-apps.}
\clientProjectHeader
{Gore Mutual}
{Django, SQL, Azure, Databricks}
\clientProjectSubItem
{Contributed to backend architecture discussions for a \textbf{Databricks → MySQL} ETL pipeline handling over \textbf{10K} records in a \textbf{Django} application, including automated data cleansing and transformation workflows.}
\clientProjectSubItem
{Implemented complex broker-facing UI features such as hierarchical views, search, and pagination, and collaborated with the design team to propose a performant UX that was approved by the product owner.}
\clientProjectHeader
{IMCO}
{Liquibase, Azure DevOps, SparkSQL}
\clientProjectSubItem
{Led the implementation of an automated schema deployment framework optimizing database migrations and improving the client's deployment efficiency by \textbf{20-30\%}.}
\clientProjectSubItem
{Collaborated with client \textbf{QA/DevOps} teams to align the framework with their critical pain points, leading to eventual adoption and received positive feedback during multiple demos.}
\resumeItemListEnd


\resumeSubheading
{Royal Bank of Canada}{Toronto, ON}
{Software Developer Co-op}{Java, SpringBoot, Maven, Jenkins}{Jan. 2023 -- Apr. 2023}
\resumeItemListStart
\resumeItem
{Enhanced existing \textbf{SpringBoot} APIs powering mainframe verification and transactions at over \textbf{4000} RBC ATMs.}
\resumeItem
{Resolved \textbf{22} critical security vulnerabilities in the codebase caused by \textbf{Maven} dependencies, twice as fast as estimated.}
\resumeItem
{Performed successful migration of legacy \textbf{SpringBoot} applications from \textbf{Java 8} to \textbf{Java 17} by rewriting incompatible code components into new syntax and updating sub-dependencies.}
\resumeItemListEnd

\resumeSubheading
{University Health Network}{Toronto, ON}
{Software Engineer Co-op/Part-Time}{Python, MSSQL, React, PHP, LaTeX}{Jan. 2022 -- Dec. 2022}
\resumeItemListStart
\resumeItem
{Developed an automated \textbf{ETL} pipeline in \textbf{Python} and \textbf{pandas} that saved \textbf{10+} research hours weekly by transforming custom clinical surveys into a normalized data model for faster visualization.}
\resumeItem
{Increased team productivity by developing reusable \textbf{Python} scripts that automated the generation of clinical result reports.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}

\projectSubHeadingListStart

\projectSubheading{\seticon{faGithub} Langchain Open Source Contribution}
{Python}
{Popular LLM Library with over \textbf{88K} stars}
{https://github.com/langchain-ai/langchain/pull/13318}
{Sep. 2023 - Dec. 2023}
\projectItemListStart
\projectItem{}
{Expanded language support in \textbf{Langchain} within the LanguageParser module to enable \textbf{Retrieval Augmented Generation (RAG)} with source code files in \textbf{12} programming languages.}
\projectItem{}
{Pull request reviewed and accepted within \textbf{2} months and merged into version \textbf{0.1.17}.}
\projectItemListEnd

\projectSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Toronto - Honors Bachelor's of Science}{Sep. 2020 -- Jun.
  2024}
{Major in Computer Science}{Specialization in Software Engineering
  Stream}{Toronto, ON}
\resumeItemListStart
\resumeItem
{\textbf{Teaching Assistant} -- \textit{CSCC09, CSCC01, CSCB07, MATA32, MATA33, MATA34, MATA36} \\ Mentored \textbf{30+} students weekly in core Computer Science concepts including \textbf{software engineering} and \textbf{web development}, improving their understanding of \textbf{Java}, \textbf{JavaScript}, and more. }
\resumeItemListEnd
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}